Adapting the MVDR to a GPU for active sonar systems of different sizes.

### 2013-01-21 ASA2013/asa2013.tex
la2pdf commit - 2013:01:21	21:57:56	(Mon21.Jan)

\documentclass[
a4paper,10pt
]{common/ica2013_2}

@@

@@

<< OUTLINE >>

@@

\section{Methods}

@@

\subsection{MVDR beamformer}

@@

@@

\section{Implementation}

@@

@@

@@

\bibliographystyle{common/jasanum}
\bibliography{../../Library/library}

>>>>

\documentclass[
a4paper,10pt
]{ica2013_2}

@@

\definecolor{tabBlue}{HTML}{AACCFF}

@@

This article is outlined as follows: In section \ref{methods} we will present the theoretical background on MVDR operated in time and frequency domain, as well as relating this to the LCA beamformer.  As we move along we aim to mention complexity issues and suggest means to overcome them, but implementational aspect will first be presented in \ref{implementation}.

@@

\section{Methods}\label{methods}

@@

\subsection{MVDR beamforming in time domain}

@@

\subsection{MVDR beamspace}

@@

\section{Implementation}\label{implementation}

% Most of the challenges we faced when porting the MVDR to a GPU are caused by a single troublesome fact: GPU prefers threads that computationally intensive but very light on memory consumption.

Throughout our work with porting the MVDR beamformer to a GPU, one issue has been particularly difficult to solve: The GPU will only perform efficiently when each computing thread is very computationally intense. This should be apparent by studying Table \ref{tabbandwidth}. It compares theoretical peak values for the memory bandwidth and arithmetic throughput for an Nvidia Quadro 6000 GPU. Looking at global memory, we note that it is only able to move 1 float for every 30 floating point numbers that the GPU is able to execute. Now, if we consider the simple equation $C=A+B$, where the ratio is 3 floats read/written for every 1 floating point operation, we realise that global memory should be avoided whenever possible. Using shared memory (L1 cache) and registers is a big step in the right direction, but this e
\begin{table}[b]\centering%\normalsize
\begin{tabular}[c]{l r r r@{:}  l}\hline
\rowcolor{tabBlue} & \multicolumn{1}{>{\columncolor{tabBlue}}c}{\bf BW$_\text{arithmetic}$} & \multicolumn{1}{>{\columncolor{tabBlue}}c}{\bf BW$_\text{memory}$} & \multicolumn{2}{>{\columncolor{tabBlue}}c}{\bf BW$_\text{memory}$/BW$_\text{arithmetic}$} \\\hline
Arithmetic throughput & 1.03 Tflop/s & & \hspace{30pt} 1 & 30 \\
Global memory & & 36 Gfloats/s & \hspace{30pt} 1 & 30 \\
Shared memory & & 257 Gfloats/s & 1 & 4 \\
Registers & & $>$1.5 Tfloats/s & $>$3 & 2~\cite{Vasilyy}
\end{tabular}
\caption{Nvidia Quadro 6000; Memory bandwidths (BW) compared to the peak arithmetic bandwidth of 1.03 TB/s.}\label{tabbandwidth}
\end{table}

@@

\begin{figure}[t]\centering%
\graphicsAI[drawing,width=\linewidth]{gfx/plot_holmengraa_L16_Navg1.pdf}%
\caption{Holmengraa.}\label{mvdr_implementation}
\end{figure}

@@

MVDR for systems with less than 32 channels. After that MVDR in beamspace.

@@

\bibliographystyle{jasanum}
% \bibliography{../../Library/library}
\bibliography{library}
